---
title: "Alcohol vs Seat choice"
author: "Luis Resendez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in.
 
 The data came from UCDavis in the 1990's.
 
$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

## Methods
In the data set by davisdata Seat is categorical variable, alcohol is numerical.

We are trying to predict alcohol consumption ~ based on seating, so we use the Numerical~Cat helper file.

## Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```


```{r}
basicCN + geom_boxplot()
```

This boxplot shows that the consumption of alcohol for the back are greater than the middle and front seats.


### Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The numerical summary also shows that the back seats 2.5 more than the middle and 3.5 more than the front seats.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is 0.000116, less than 0.05 so we reject the null hypothesis.  
There is a difference in alcohol consumption based on where people sit.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

In the TUkey HSD plot also shows middle and back drink more than the front.



## Conclusions

The null hypothesis stating that "alcohol consumption is not dependent on row seating" was tested using Numerical~Cat.rmd program and information from UCDavis where data set by davisdata Seat is categorical variable, alcohol is numerical.The results showed a p-value of 0.000116, which is less than the significance level of 0.05. Therefore, we rejected the null hypothesis and conclude that alcohol consumption is indeed dependent on row seating.


