---
title: "Alcohol vs Seat choice"
author: "Luis Resendez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in.
 
 The data came from UCDavis in the 1990's.
 
$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

## Methods
In the data set by davisdata Seat is categorical variable, alcohol is numerical.

We are trying to predict alcohol consumption ~ based on seating, so we use the Numerical~Cat helper file.

## Results

## Descriptive Results

## Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that the consumption for the back seats have way more alcohol than the middle and front seats.


### Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


### Inferential Tests

### Conclusions



## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests
The p-value is 0.000116, less than 0.05 so we reject the null hypothesis 
## Conclusions
There is a difference in alcohol consumption based where people sit.
